---
title: Regular Vegetation Patterns
author: Karl Kästner et al.
---
Red : Anisotropic Patterns
<br>
Blue : Isotropic Patterns

<style type="text/css">
.main-container {
  width: 100%;
  max-width: 100%;
  height: 100%;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r load-packages, echo=F, message=F, warning=F}
library(plyr)
library(dplyr)
library(terra)
library(sf)
library(leaflet)
library(leafpop)
library(knitr)
library(DT)
knitr::opts_chunk$set(cache=T, echo=F, message=F, warning=F)
```


```{r read-data, echo=F, cache=T}
aniso <- read_sf("mat/vegetation-patterns-anisotropic-analyzed-poly.shp")
iso   <- read_sf("mat/vegetation-patterns-isotropic-analyzed-poly.shp")
```


```{r concatenate-data, echo=F, fig.width=12, fig.height=12, out.width="100%", out.height="100vh", cache=T}
#data <- bind_rows(aniso, iso)
data <- rbind(aniso, iso)
data = data[1:10,]

x = c();
y = c();
options(warn=-1)
for (i in seq(1,nrow(data)))
{
  p = st_centroid(data[i,])
  x[i] = p$geometry[[1]][1]
  y[i] = p$geometry[[1]][2]
}
options(warn=0)
print("assigning colours")
color <- c("red", "blue")[data$isisotropic+1]

print("assingning data values")
data$x = x
data$y = y
data$id = NULL
data$continent = NULL
data$L_eff_r = NULL
data$L_eff_x = NULL
# area_m2 	1.546844e+05 
data$contrast=NULL
data$coverage=NULL
data$filename=NULL
data$intS_hp_sig=NULL
data$isisotropic=NULL
#p_periodic
data$p_S_hp=NULL
data$region_id=NULL
data$region_str = NULL
data$regulari_r=NULL
data$regulari_x=NULL
data$regulari_y=NULL
data$runtime1=NULL
#20	date
#21	waveleng_r
#22	waveleng_x
#23	qc_passed

print("generating leaflet")
leaflet(data) %>%
  addProviderTiles("Esri.WorldImagery", options = tileOptions(maxZoom = 17)) %>%
  addPolygons(label = ~region, fill = "transparent",
              popup=popupTable(tibble(data) %>% select(-geometry)), color =color, fillOpacity = 0)

```

region     : World region the pattern was assigned too<br>
area_m2    : area of the polygon circumscribing the pattern<br>
p_periodic : p-value of the periodicity test<br>
date       : date the satellite image was downloaded<br>
waveleng_r : charateristic wavelength of isotropic patterns (radial density)<br>
waveleng_x : characteristic wavelength of anisotropic patterns (x-density)<br>
qc_passed  : Quality check, only patterns with value 1 are included in the analysis

---
#```{r}
#datatable(data)
#```
---

